---
title: "pml"
author: "Muskan"
date: "10/20/2020"
output:
  word_document: default
  html_document: default
---

Details regarding the assignment:

So basically for the analysis of this project, I have collected some databases from NIKE,FITBIT,etc. These datasets I will be using for my final project of Practical Machine Learning.

So basically we are checking whether the exercises are being done with utmost precision or not and also we check whether they are int the correct order.'

Step 1 of this project:Dataset Loading
Step 2:Data is being processed
Step 3:the next step would be exploration of the dataset.
Step 4:Now we need to predict the model we will be selecting to get the output.
Step 5:Now, we will be predicting the data on the given dataset for testing.





```{r}
library(caret)

library(knitr)

library(data.table)

library(rpart.plot)

library(rpart)

library(gbm)

library(ggplot2)

library(corrplot)

```

Exploring and cleaning the data.

```{r}
tU <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

traU  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

d_tst <- read.csv(url(tU))

d_tr <- read.csv(url(traU))




```

In this step we would be cleaning the data.
```{r}
train_dat <- d_tr[, colSums(is.na(d_tr)) == 0]

test_d <- d_tst[, colSums(is.na(d_tst)) == 0]


```

Next step is prediction of the data. So 30% is used for testing our dataset and 70% for training the set we are using in this project.

```{r}
train_dat <- train_dat[, -c(1:7)]

test_d <- test_d[, -c(1:7)]

dim(train_dat)


```
in this step we are deleting the variables that are non-zero referred to as 'nz' in this code
```{r}
set.seed(1234)

dtrain <- createDataPartition(d_tr$classe, p = 0.7, list = FALSE)


train_dat <- train_dat[dtrain, ]

test_d <- train_dat[-dtrain, ]

dim(train_dat)

dim(test_d)

```

```{r}

nZ <- nearZeroVar(train_dat)

train_dat <- train_dat[, -nZ]

test_d <- test_d[, -nZ]

dim(train_dat)

dim(test_d)

```

```{r}

p_cor <- cor(train_dat[, -53])

corrplot(p_cor, order = "FPC", method = "color", type = "upper", tl.cex = 0.8, tl.col = rgb(0, 0, 0))

```
the corr. predic. are with the dark colour intersec.This is the observation in this case.

Next step is the building of our model for the dataset we are using.
The Algorithms we will be using are trees and random forests for the prediction part.

```{r}
set.seed(20000)

tr <- rpart(classe ~ ., data=train_dat, method = "class")

rpart.plot(tr)


```

Validation of the model
```{r}
modp <- predict(tr, test_d, type = "class")

ab <- confusionMatrix(modp, test_d$classe)

ab

```

```{r}

plot(modp)


```

Lets apply two models in this case:
First is General boosted model.
Second is gbm model.

```{r}
set.seed(10000)

cand_gbm <- trainControl(method = "repeatedcv", number = 5, repeats = 1)

val <- train(classe ~ .,data=train_dat, method = "gbm", trControl = cand_gbm, verbose = FALSE)
val$finalModel

```

Conclusion:
Prediction that someone did the exercise order wise.
Ananlysing using some techniques like cross validation.
This is the end of my project.Hope you find it useful and i would like to thank the Profs. for helping me out!!
I am attaching the outputs as well for further use if required.





